\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}


\begin{document}
\title{Book summary and Ideas}
\author{Erwan 'Feideus' Ulrich -- the Will-be Best Story Teller }
\maketitle

\section{Characters}
\begin{itemize}
\item{Character 1}
	\begin{itemize}
	\item{Main: Male, about 25, entered the army couple years ago}
	\item{Name ?}
	\item{Background: common folks parents, 2 sisters and 1 brother}
	\item{Skills: Good swordsman, too frank, carver, poor handwriting, very bad speaking capacities, cheerful, straight oriented}
	\item{physical: Dark curly haired blue eyed, muscular, short, large scar from neck to shoulder, rather hairy}
	\end{itemize}

\item{Character 2}
	\begin{itemize}
	\item{Main: male ,27, son of a noble family close to the king. Fled to avoid arranged marriage}
	\item{name ?}
	\item{Background: rich familly, afraid of birds (and forest in general), 1 sister.}
	\item{Skills: very cultivated, blade master, terrible cook, plays music (instrument ? (flute ?)), very straight hair  }
	\item{short, chatain, pale, thin, delicate skin (apart from hands)}
	\end{itemize}
\end{itemize}

\section{World Context}
\begin{itemize}
\item{Magic (manifestation after long usage as colored stribes on arms and legs)}
\item{Big countries + small countries (story takes place between 2 small countries )}
\item{Everybody plots to take over or gain influence}
\item{Some known creatures, some are specific to this world.}
\item{peuple uniquement par des humanoides}
\item{Magic wakes up at some point in life or never}
\item{hasn't been at war for decades}
\item{magic doesnt intervene in this story line}
\item{The people is very poor}
\item{Spend most of their money in "pubs" to forget their misery}
\item{General feeling of depression and sadness.}
\item{Lower class people are being bullied by the \underline{magic class} \underline{noble class}, \underline{royalty}}
\item{Power is divided between magic, religion, nobles, royalty (king has more power than in the past since the land has been in peace for decades. This might change in futures story lines)}
\end{itemize}

\section{Plot summary}
	\subsection{Beginning}
		\begin{itemize}
		\item{Description of characters}
		\item{Description of the world}
		\item{1st Character goes on "vacations" at his parents}
		\item{Has to solve a pub fight which goes wrong due to poor diplomacy}
		\end{itemize}
	\subsection{Core of the story}
		\begin{itemize}
		\item{Primary characters has to go back cause he fucked up}
		\item{Meets second character after almost getting into a fight on the way back}
		\item{Second character lies about his identity (claims to be a wanderer)}
		\item{They go together at the headquaters of the military organization (get attacked by thieves of the way sent by the military chef sneakily). 2nd characters shows great sword skills.}
		\item{1st character gets sent back to fix the situation that escalated in the mean time into city rivality}
		\item{2nd character talks to the lord which decides to try to negociate with the other lord and hands them over to rival for peace.}
		\item{1st character's brother tries to free him and gets mutilated. the war between lords starts.}
		\item{.......add story elements here there........}
		\item{Ending: Final battle between the two countries where the maire of the town and the head of the military were corrupted by the ennemy country. head of the military gets killed by the 1st character.}

		\end{itemize}
	\subsection{Ending}
\end{document}